### 2017-04-10 oj.tex
init

\documentclass{beamer}

\usepackage[utf8]{inputenc}
%\usepackage{adjustbox}
\usepackage[export]{adjustbox}
\usepackage{booktabs}
%\usepackage{ctex}
\usepackage{graphicx}
\usepackage{subcaption}

\captionsetup{compatibility=false}

\graphicspath{ {images/} }

\usetheme{Madrid}

\title[OJ user behavior]{The User Behavior On Online Judge Website }
\author[yiyuezhuo]{yueyi zhuo}
\institute[SICNU]{School of Mathematical,Sichuan Normal University}
\date{2017}

\begin{document}

\frame{\titlepage}

\begin{frame}

\frametitle{What is online judge(oj)?}

An online judge is an online system to test programs in programming contests. They are also used to practice for such contests. Many of these systems organize their own contests.

The system can compile and execute code, and test them with pre-constructed data. Submitted code may be run with restrictions, including time limit, memory limit, security restriction and so on. The output of the code will be captured by the system, and compared with the standard output. The system will then return the result. When mistakes were found in a standard output, rejudgement using the same method must be made.

Online Judges have ranklists showing users with the biggest number of accepted solutions and shortest execution time for a particular problem. \footnote{Wikipedia https://en.wikipedia.org/wiki/Online\_judge}

\end{frame}

\begin{frame}
\frametitle{Euler project}
\includegraphics[scale=0.55]{euler-oj.png}
\end{frame}

\begin{frame}
\frametitle{leetcode OJ}
\includegraphics[scale=0.4]{leetcode-oj.png}
\end{frame}

\begin{frame}
\frametitle{Sicnu OJ}
\includegraphics[scale=0.5]{SICNU-oj.png}
\end{frame}

\begin{frame}
\frametitle{Some problem in Real world}

The data listed on the list looks very interesting. These're a number of insights for user behavior which 
can generalize to online education service. For example:

Why number of solved sequence looks like this? If we provide online education product as same as those oj, 
and observe such series, does it mean our product fail or extra-success?

\begin{figure}[h]

\begin{subfigure}{0.45\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq1.png} 
\caption{Solved number series}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{0.45\textwidth}
\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq2.png}
\caption{Log solved number series}
\label{fig:subim2}
\end{subfigure}

\caption{Caption for this figure with two images}
\label{fig:image2}
\end{figure}

\end{frame}

\begin{frame}

\frametitle{Identify}

Is it signicant to put difficulty problem on the behind those easy problem 
if we want keep our user happy and not be shocked by those monster? It make sense
for online education to maintain user interest in their study process. For technically speaking:
According to data, do we observe the fact that a hard problem cause a temporary 
or continued solved number decrease,
although we have controlled other effect? 
How do we control other effect to identify the shock from hard problem?

There's a baseline regression have been run to

\end{frame}

\begin{frame}

\frametitle{Model 1}

$$
solve_i = \beta_0 + \beta_1 id_i + \beta_2 diff_i + \epsilon_i
$$

where $id_i$ is the id of problem $i$, $diff_i$ is difficulty measure given by Project Euler.

\begin{center}
\scalebox{0.5}[0.5]{
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}    &      solve       & \textbf{  R-squared:         } &    0.331  \\
\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &    0.325  \\
\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &    63.95  \\
\textbf{Date:}             & Mon, 10 Apr 2017 & \textbf{  Prob (F-statistic):} & 2.68e-23  \\
\textbf{Time:}             &     22:53:04     & \textbf{  Log-Likelihood:    } &  -3224.6  \\
\textbf{No. Observations:} &         262      & \textbf{  AIC:               } &    6455.  \\
\textbf{Df Residuals:}     &         259      & \textbf{  BIC:               } &    6466.  \\
\textbf{Df Model:}         &           2      & \textbf{                     } &           \\
\textbf{Covariance Type:}  &    nonrobust     & \textbf{                     } &           \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
}
\scalebox{0.5}[0.5]{
\begin{tabular}{lccccc}
\toprule
                   & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{Intercept} &    9.401e+04  &     6678.292     &    14.077  &         0.000        &      8.09e+04  1.07e+05       \\
\textbf{id}        &    -479.7585  &       90.521     &    -5.300  &         0.000        &      -658.008  -301.509       \\
\textbf{diff}      &     -60.2227  &      266.704     &    -0.226  &         0.822        &      -585.406   464.961       \\
\bottomrule
\end{tabular}
}
\scalebox{0.5}[0.5]{
\begin{tabular}{lclc}
\toprule
\textbf{Omnibus:}       & 270.575 & \textbf{  Durbin-Watson:     } &    0.077  \\
\textbf{Prob(Omnibus):} &   0.000 & \textbf{  Jarque-Bera (JB):  } & 8178.806  \\
\textbf{Skew:}          &   4.299 & \textbf{  Prob(JB):          } &     0.00  \\
\textbf{Kurtosis:}      &  28.986 & \textbf{  Cond. No.          } &     317.  \\
\bottomrule
\end{tabular}
}
\end{center}

\end{frame}

\begin{frame}

We can see the estimated effect of diff is negative but not be signicant. The result does not adapt by theory,
and DW statistic is too low which imply possibility that autocorrelation exist in model. 
Let we try to apply log transform on $solve$ to reduce the effect and to make estimated value more precise.

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model1-resid.png}
\caption{Plot of residuals of model 1}
\end{figure}

\end{frame}

\begin{frame}

\frametitle{Model 2}

$$
\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff_i + \epsilon_i
$$

\begin{center}
\scalebox{0.5}[0.5]{
\begin{tabular}{lclc}
\toprule
\textbf{Dep. Variable:}    &    log(solve)    & \textbf{  R-squared:         } &     0.943  \\
\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.943  \\
\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     2150.  \\
\textbf{Date:}             & Mon, 10 Apr 2017 & \textbf{  Prob (F-statistic):} & 4.94e-162  \\
\textbf{Time:}             &     23:27:00     & \textbf{  Log-Likelihood:    } &   -128.21  \\
\textbf{No. Observations:} &         262      & \textbf{  AIC:               } &     262.4  \\
\textbf{Df Residuals:}     &         259      & \textbf{  BIC:               } &     273.1  \\
\textbf{Df Model:}         &           2      & \textbf{                     } &            \\
\textbf{Covariance Type:}  &    nonrobust     & \textbf{                     } &            \\
\bottomrule
\end{tabular}
%\caption{OLS Regression Results}
}
\scalebox{0.5}[0.5]{
\begin{tabular}{lccccc}
\toprule
                   & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
\midrule
\textbf{Intercept} &      11.4369  &        0.049     &   232.406  &         0.000        &        11.340    11.534       \\
\textbf{id}        &      -0.0081  &        0.001     &   -12.179  &         0.000        &        -0.009    -0.007       \\
\textbf{diff}      &      -0.0407  &        0.002     &   -20.685  &         0.000        &        -0.045    -0.037       \\
\bottomrule
\end{tabular}
}
\scalebox{0.5}[0.5]{
\begin{tabular}{lclc}
\toprule
\textbf{Omnibus:}       & 117.312 & \textbf{  Durbin-Watson:     } &     0.197  \\
\textbf{Prob(Omnibus):} &   0.000 & \textbf{  Jarque-Bera (JB):  } &   466.808  \\
\textbf{Skew:}          &   1.888 & \textbf{  Prob(JB):          } & 4.30e-102  \\
\textbf{Kurtosis:}      &   8.339 & \textbf{  Cond. No.          } &      317.  \\
\bottomrule
\end{tabular}
}
\end{center}

\end{frame}

\begin{frame}

New model make $diff$ significant but DW statistic still be too small (0.197 from 0.07). 
Since $diff$ is not a real quantity index which take value as 5, 10, etc for no reason,
we replace it to two new dummy variables $diff\_mid$ and $diff\_hard$. 
$diff\_mid_i=1$ if $diff > 25$,else $diff\_mid_i=0$.
$diff\_hard_i=1$ if $diff > 50$,else $diff\_hard_i=0$.

\begin{figure}[h]
\includegraphics[width=0.5\textwidth, inner]{model2-resid.png}
\caption{Plot of residuals of model 2}
\end{figure}

\end{frame}

\end{document}

### 2017-04-11 oj.tex
add model

@@
 
-An online judge is an online system to test programs in programming contests. They are also used to practice for such contests. Many of these systems organize their own contests.
+An online judge is an online system to test programs in programming contests. 
+They are also used to practice for such contests. Many of these systems organize their own contests.
 
@@
 The output of the code will be captured by the system, and compared with the standard output. 
-The system will then return the result.
-When mistakes were found in a standard output, rejudgement using the same method must be made.
+The system will then return the result. When mistakes were found in a standard output, 
+rejudgement using the same method must be made.
 
-Online Judges have ranklists showing users with the biggest number of accepted solutions and shortest execution time for a particular problem.
-\footnote{Wikipedia https://en.wikipedia.org/wiki/Online\_judge}
+Online Judges have ranklists showing users with the biggest number of accepted solutions and shortest 
+execution time for a particular problem. \footnote{Wikipedia https://en.wikipedia.org/wiki/Online\_judge}
 
@@
 \caption{Solved number series}
-\label{fig:subim1}
+\label{fig:f1}
 \end{subfigure}
@@
 \caption{Log solved number series}
-\label{fig:subim2}
+\label{fig:f2}
 \end{subfigure}
@@
 
-There's a baseline regression have been run to
+There's a regression have been run as baseline.
 
@@
 \caption{Plot of residuals of model 1}
+\label{fig:f3}
 \end{figure}
@@
 
+The only change of model 2 is that dependent variable $solve$ is transform to $log(solve)$.
 $$
@@
 \caption{Plot of residuals of model 2}
+\label{fig:f4}
 \end{figure}
@@
 
+\begin{frame}
+
+\frametitle{Model 3}
+
+$$
+\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff_mid + \beta_3 + diff_hard + \epsilon_i
+$$
+
+\begin{center}
+\scalebox{0.5}[0.5]{
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}    &    log(solve)    & \textbf{  R-squared:         } &     0.907  \\
+\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.906  \\
+\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     841.8  \\
+\textbf{Date:}             & Tue, 11 Apr 2017 & \textbf{  Prob (F-statistic):} & 6.87e-133  \\
+\textbf{Time:}             &     14:38:30     & \textbf{  Log-Likelihood:    } &   -192.36  \\
+\textbf{No. Observations:} &         262      & \textbf{  AIC:               } &     392.7  \\
+\textbf{Df Residuals:}     &         258      & \textbf{  BIC:               } &     407.0  \\
+\textbf{Df Model:}         &           3      & \textbf{                     } &            \\
+\textbf{Covariance Type:}  &    nonrobust     & \textbf{                     } &            \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+}
+\scalebox{0.5}[0.5]{
+\begin{tabular}{lccccc}
+\toprule
+                           & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{Intercept}         &      11.2770  &        0.066     &   169.869  &         0.000        &        11.146    11.408       \\
+\textbf{diff\_mid[T.True]}  &      -1.0259  &        0.102     &   -10.088  &         0.000        &        -1.226    -0.826       \\
+\textbf{diff\_hard[T.True]} &      -0.6194  &        0.092     &    -6.731  &         0.000        &        -0.801    -0.438       \\
+\textbf{id}                &      -0.0124  &        0.001     &   -16.695  &         0.000        &        -0.014    -0.011       \\
+\bottomrule
+\end{tabular}
+}
+\scalebox{0.5}[0.5]{
+\begin{tabular}{lclc}
+\toprule
+\textbf{Omnibus:}       & 32.712 & \textbf{  Durbin-Watson:     } &    0.774  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &   45.065  \\
+\textbf{Skew:}          &  0.810 & \textbf{  Prob(JB):          } & 1.64e-10  \\
+\textbf{Kurtosis:}      &  4.225 & \textbf{  Cond. No.          } &     501.  \\
+\bottomrule
+\end{tabular}
+}
+\end{center}
+
+\end{frame}
+
+\begin{frame}
+
+The DW statistic looks better than using $diff$ directly. But if we inspect the the plot of residual of model3, 
+the same pattern is weaken while there aren't fundamental change what we expect.
+
+\begin{figure}[h]
+\includegraphics[width=0.5\textwidth, inner]{model3-resid.png}
+\caption{Plot of residuals of model 3}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}
+
+\frametitle{Why the residual pattern occur? The road to user personas. }
+
+Although we can run a segmented regression, but more fundamental origin is interesting to investigate.
+A idea to model this phenomenon is to try to decompose user into distinct groups
+who act differently in problem solving process.
+
+For example, the "light" user may solve first few problems and then leave while the "hard core" 
+user would try solve many problem until their interest wore off and nerd would like to solve prolbem
+labeled in hardest. 
+These effects are mixed and hard to distinguish if we only consider the infomation given by OJ website.
+
+For example, the number of hit of chinese translation of description of origin problem is a variable relate 
+solved number. In fact, we can run a parallel model on hit data.
+
+\end{frame}
+
 \end{document}

### 2017-04-11 oj.tex
complete ppt

@@
 
-\frametitle{What is online judge(oj)?}
+\frametitle{What is online judge(OJ)?}
 
@@
 \begin{frame}
-\frametitle{Euler project}
+\frametitle{Project Euler}
 \includegraphics[scale=0.55]{euler-oj.png}
@@
 
-The data listed on the list looks very interesting. These're a number of insights for user behavior which 
+The data listed on the table looks very interesting. These're a number of insights for user behavior which 
 can generalize to online education service. For example:
 
-Why number of solved sequence looks like this? If we provide online education product as same as those oj, 
+Why the sequence of number of solved looks like this? If we provide online education product as same as those oj, 
 and observe such series, does it mean our product fail or extra-success?
@@
 
-Is it signicant to put difficulty problem on the behind those easy problem 
-if we want keep our user happy and not be shocked by those monster? It make sense
+Is it signicant to put difficult problem on the behind those easy problem 
+if we want keep our user satisfactory and not be shocked by excess hard problem? It make sense
 for online education to maintain user interest in their study process. For technically speaking:
 According to data, do we observe the fact that a hard problem cause a temporary 
-or continued solved number decrease,
-although we have controlled other effect? 
-How do we control other effect to identify the shock from hard problem?
+or continued solved number decrease, although we have controlled other effect?
 
-There's a regression have been run as baseline.
+How do we control other effect to identify the shock from hard problem? The econometric model might help, 
+following regression models have been run as baseline to lead to thee problem that we try to survey.
 
@@
 
-We can see the estimated effect of diff is negative but not be signicant. The result does not adapt by theory,
-and DW statistic is too low which imply possibility that autocorrelation exist in model. 
+We can see the estimated effect of $diff$ is negative but not be signicant. 
+While the result does not adapt for theory,
+DW statistic is too low which imply possibility that autocorrelation exist in model. 
 Let we try to apply log transform on $solve$ to reduce the effect and to make estimated value more precise.
@@
 $$
-\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff_mid + \beta_3 + diff_hard + \epsilon_i
+\log(solve_i) = \beta_0 + \beta_1 id_i + \beta_2 diff\_mid + \beta_3 diff\_hard + \epsilon_i
 $$
@@
 The DW statistic looks better than using $diff$ directly. But if we inspect the the plot of residual of model3, 
-the same pattern is weaken while there aren't fundamental change what we expect.
+the same pattern is weaken while there aren't fundamentally changed to what we expect.
 
@@
 
-\frametitle{Why the residual pattern occur? The road to user personas. }
+\frametitle{What construct the residual pattern? The road to user personas. }
 
@@
 A idea to model this phenomenon is to try to decompose user into distinct groups
-who act differently in problem solving process.
+who acts differently in problem solving process.
 
@@
 user would try solve many problem until their interest wore off and nerd would like to solve prolbem
-labeled in hardest. 
-These effects are mixed and hard to distinguish if we only consider the infomation given by OJ website.
+labeled as hardest.
 
-For example, the number of hit of chinese translation of description of origin problem is a variable relate 
-solved number. In fact, we can run a parallel model on hit data.
+How to esimate these latent factor? The solved sequence may be too weak to apply identification. 
+Fortunately, some extra-date have been collected for the goal.
+
+%These effects are mixed and hard to distinguish if we only consider the infomation given by OJ website.
+
+%For example, the number of hit of chinese translation of description of origin problem is a variable relate 
+%solved number. In fact, we can run a parallel model on hit data.
+
+\end{frame}
+
+\begin{frame}
+
+\frametitle{Extended Data Structure and Cross Estimation}
+
+These's a chinese translation website that provide problem description translation for original problem.
+Obviously, the hit count of problem is a important factor to measure problem real difficulty taken by to compare 
+hit and solved number. Sadly, Project Euler dont't provide this measure directly, 
+but the hit prodived by translation post would be a nice proxy variable. Of course the method cause new problem.
+Someone may looks chinese translation post for their poor English(like me), 
+thus if we equally weight eveny posts, then the problem hard to read will be exaggerated on their difficulty estimated.
+Against this challenge, I collect the text length of description in both English(origin) and Chinese(translation) version,
+although the difficulty in readability but not problem may be caused by some vague statement or confusing grammar
+that can't be caught by text length.
+
+\end{frame}
+
+\begin{frame}
+
+If we assume that these OJ shares same user and their behavior distribution, 
+we can estimate these hidden parameters on a more horizon space, instead of only to observe one sequence 
+as the only one sample to model, and use data only not hold in one OJ but hold in other. For example, 
+as previous images, Project Euler doesn't include Acceptance index, but the two others does, hence we can use the two
+others index to fill Project Euler one. How excellent idea! Thanks internet prodive so many website which 
+provide same and distinct index from their "nature experiment". Big data equip us with these advanced tool
+to investigate world that hided in past.
+
+The current data structure looks like this:
+
+\begin{tabular}{lrrrrrrr}
+\toprule
+{} &  id &  content &  des\_len &  diff &    hit &   solve &  t\_content \\
+\midrule
+0 &   1 &      187 &       25 &     5 &  13792 &  537234 &         85 \\
+1 &   2 &      312 &       32 &     5 &   7571 &  438350 &        135 \\
+2 &   3 &      111 &       17 &     5 &   6364 &  317208 &         65 \\
+3 &   4 &      209 &       20 &     5 &   5414 &  285419 &        101 \\
+4 &   5 &      206 &       24 &     5 &   4627 &  297082 &         70 \\
+\bottomrule
+\end{tabular}
+
+\end{frame}
+
+\begin{frame}
+
+\frametitle{The Power of Cross Estimation, A Example}
+
+Let's see a example about the power in cross estimation. The following is hit sequence, what made the abrupt decrease?
+Compare to original sequence, we can't see same pattern. For any reason, these's a change to run regression discontinuity
+to identify some effect that are hard to identify usually.
+
+\begin{figure}[h]
+
+\begin{subfigure}{0.45\textwidth}
+\includegraphics[width=0.9\linewidth, height=4cm]{hit-seq.png} 
+\caption{Hit number series}
+\label{fig:f1}
+\end{subfigure}
+\begin{subfigure}{0.45\textwidth}
+\includegraphics[width=0.9\linewidth, height=4cm]{solved-seq2.png}
+\caption{Log solved number series}
+\label{fig:f2}
+\end{subfigure}
+
+%\caption{Caption for this figure with two images}
+\label{fig:image2}
+\end{figure}
 

### 2017-04-28 paper.tex
start writing paper

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\graphicspath{{images/}}

\title{The User Behavior On Online Judge Website}
\author{yueyi zhuo}
%\institute{School of Mathematical,Sichuan Normal University}
\date{2017}

\begin{document}

\maketitle

\begin{abstract}

Abstract content.

\end{abstract}

\section{Introduction}

In 2016 Spring Festival, I solve some problems in Project Euler 
\footnote{In fact, I solve 70+ problems before my interest fade.}, 
which may be most famous online judge 
in Internet except Leetcode. I have noticed the interesting data structure related with rank and difficulty.
But I lacked enough powerful statistic tool to process and model it. 
In fact, I model it as a ordinary least squard which is not understood by me in the time. In the naive period,
linear regression model seems like a poor black box model that often be meeted in Machine Learning algorithm.

\section{Motivation}

Motivation content.

\end{document}

### 2017-04-30 paper.tex
writing paper...

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
 \graphicspath{{images/}}
@@
 
+Now, partly because of study of course of Econometric, I totally understand the random model and the instance,
+linear regression. 
+Right, there're some random variable constrained by expectation function sharing same parameters, that's all.
+A specific linear regression model correspond to many latent models specified indepent variable distribution,
+but their expectation function are same. This lead to same result from estimator and model test.
+
+My insight is given by some external user comment about their usage they use OJ. 
+Someone claim that thay solve problem by order of the number of solved, but I solve problem by order of ID.
+I'm fascinated by thinking that how to identify the percent of two type if we assume only the two type exists.
+Since the particular problem represent a more general problem set, I would like to treat it as a bridge to that.
+
+Let's formulate my ealiest idea, there're $N$ problems, $n$ solver. Let 
+$s_{ij} \in \{ 0,1 \} \quad i \in \{ 1,\dots,n \} \; j \in \{ 1,\dots,N \}$ be whether solver $i$ solve the problem $j$.
+So fixing solver $i$, we assume binary random vector $s_i = ( s_{i1} s_{i2} \dots s_{iN} )^T$ 
+can be divided into some group which is determined by a specific distribution and they're independent.
+Specially, I define the distribution $D_1$ which follow order of ID:
+
+\begin{align*} % Notice align or align* is not used in math mode. They can be directly include in paragraph(normal) mode.
+P(s_{i1} = 1) = p \\
+P(s_{ij} = 1 | s_{i,j-1}=0) = 0 \\
+P(s_{ij} = 1 | s_{i,j-1}=1) = p
+\end{align*}
+
+and define $D2$ which follow order of the number of solved:
+
+\begin{align*}
+P(s_{i,r(1)} = 1) &= p \\
+P(s_{i,r(j)} = 1 | s_{i,r(j-1)}=0) &= 0 \\
+P(s_{i,r(j)} = 1 | s_{i,r(j-1)}=1) &= p
+\end{align*}
+
+in which $r(i)$ is function that map the the rank of number of solved to id
+(e.g. r(10)=20 means that the rank of number of solved of 20th problem is 10).
+Obviously we can replace $r(i)$ to any onther order that mean some interesting thing to get other distribution.
+
+Let $n_1,n_2$ be the individual number that follows $D_1,D_2$, hence $n_1+n_2=n$. Unfortunately, we only can 
+observe the sum of every sample sequence:
+
+$$
+S_j = \sum_{i=1}^n s_{ij}
+$$
+
+Our data is only the a obseration of statistic $S_j$ exactly. It looks like:
+
 \section{Motivation}

### 2017-05-01 paper.tex
writing paper...

@@
 \usepackage{graphicx}
-\usepackage{amsmath}
+\usepackage{subfigure}
+\usepackage{amsmath,amssymb}
 \graphicspath{{images/}}
+
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator{\E}{\mathbb{E}}
 
@@
 But I lacked enough powerful statistic tool to process and model it. 
-In fact, I model it as a ordinary least squard which is not understood by me in the time. In the naive period,
+In fact, I model it as a ordinary least square which is not understood by me in the time. In the naive period,
 linear regression model seems like a poor black box model that often be meeted in Machine Learning algorithm.
@@
 
-and define $D2$ which follow order of the number of solved:
+and define $D_2$ which follow order of the number of solved:
 
@@
 
-$$
+\[
 S_j = \sum_{i=1}^n s_{ij}
-$$
+\]
 
-Our data is only the a obseration of statistic $S_j$ exactly. It looks like:
+We have only data that is once obseration of statistic $S_j$ exactly. It looks like:
+
+\begin{figure}[h]
+
+\centering
+
+\subfigure[Solved number series]{\label{fig:a}\includegraphics[width=0.49\linewidth]{solved-seq1.png}}
+\subfigure[Log solved number series]{\label{fig:b}\includegraphics[width=0.49\linewidth]{solved-seq2.png}}
+
+\end{figure}
+
+The data is scraped from Project Euler \footnote{Project Euler website: https://projecteuler.net/archives }
+, my problem answers, crawler program and basis analysis is hosted on GitHub \footnote{https://github.com/yiyuezhuo/euler }
+This is a screenshot for Project Euler website:
+
+\includegraphics[scale=0.55]{euler-oj.png}
+
+Given $n_1,n_2,p$, we can determine a model like we talk above. 
+We can specify these values througn minimizing the squard loss function:
+
+\[
+\min_{n_1,n_2,p} \sum_{j=1}^N (S^*_j - \E(S_j))^2
+\]
+
+In which $S^*_j$ is real value, $S_j$ is random variable defined by model and $n_1,n_2,p$
+
+We would like a model taking more statistic manner instead of only fitting function. 
+Thus we assume that the model is \textit{real} 
+\footnote{As so often happens, some funny Econometric model claim they're real, 
+otherwise statistic model will reduce to awkward explore method.} 
+and add a convenient noise term  $\epsilon_j$  to all $S_j$ to let our model can generate(sample) 
+any possible sequence \footnote{Anyway, a pure noise model can do it too.}.
+
+\begin{align*}
+S_j = \sum_{i=1}^n s_{ij} + \epsilon_j \\
+\epsilon_j \sim F \quad i.i.d 
+\end{align*}
+
+In which $F$ is a integer distribution that can take binomial distribution or something.
+
+\[
+\E(S_j) = \sum_{i=1}^n \E(s_{ij}) + \E(\epsilon_j) = \sum_{i=1}^{n_1} p^j + \sum_{i=n_1+1}^n p^{r(j)}
+= n_1 p^j + n_2 p^{r(j)}
+\]
+
+and apply least expectation loss rule, very frequentist:
+
+\[
+\hat{n_1},\hat{n_2},\hat{p} = \argmin_{n_1,n_2,p} \E\sum_{j=1}^N (S_j - \hat{S_j})^2
+\]
+
+In which $\hat{S_j} = \E(S_j | \hat{n_1},\hat{n_2},\hat{p})$.
+
+Unfortunately, this nonlinear form can't be transformed to linear form directly. Temporarily, 
+we constrain $n_2 = 0$, then $n_1 = n$, then the $\E(S_j)$ reduce to:
+
+\[
+\E{S_j} = n p^j
+\]
+
+and
+
+\[
+\log \E(S_j) = \log n + j \log(p)
+\]
+
+Well, so we can estimate $n,p$ by estimating $\log(n),\log(p)$ by running ordinary least square method to 
+minimize the objective function \footnote{Alrough I feel that this conversion is not strict true, since
+it assign different weights on every data point.}:
+
+\[
+\min_{\hat{n},\hat{p}} \sum_{j=1}^N ( S_j - (\log(\hat{n}) + j \log(\hat{p})) )
+\]
+
+For the real data, the estimated results are:
+
+\[
+\hat{n} = 95132.76 \quad \hat{p} = 0.98002
+\]
+
+The $\hat{n}$ looks too small and $\hat{p}$ looks too big as we notice the quick fall of sequence head that
+can not be expressed the too small $\hat{p}$ as the fit graph illustrate:
+
+\includegraphics[scale=0.55]{simple-fit.png}
+
+Since the fitting is dominated by the tail data, the rift implies that our model is too weak to express 
+the mechanism behind the data.
+
+We can verify this by to regress data chunks separately, 
+obviousily if the model is true, $\hat{p}$ will only change little subject to random noise. 
+Below results are obtained by taken first $1/10$ data and last $9/10$ data separately:
+
+\[
+\hat{p_1} = 0.9275 \quad \hat{p_2} = 0.9824
+\]
+
+% Let us merge the two fitting result into a unique figure:
 

### 2017-05-11 paper.tex
well deadline is coming...

@@
 \usepackage{amsmath,amssymb}
+\usepackage[export]{adjustbox}
+\usepackage{booktabs}
+%\usepackage{subcaption}
 \graphicspath{{images/}}
@@
 Since the particular problem represent a more general problem set, I would like to treat it as a bridge to that.
+
+\section{The order model}
 
@@
 \[
-\min_{\hat{n},\hat{p}} \sum_{j=1}^N ( S_j - (\log(\hat{n}) + j \log(\hat{p})) )
+\min_{\hat{n},\hat{p}} \sum_{j=1}^N ( \log{S_j} - (\log(\hat{n}) + j \log(\hat{p})) )
 \]
 
-For the real data, the estimated results are:
+The OLS model is:
+
+\[
+S_j = \log(n) + \log(p) j + \epsilon_j
+\]
+
+The result estimated by OLS are:
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}    &    log(solve)    & \textbf{  R-squared:         } &     0.849   \\
+\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.849   \\
+\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     1466.   \\
+\textbf{Date:}             & Thu, 11 May 2017 & \textbf{  Prob (F-statistic):} & 7.30e-109   \\
+\textbf{Time:}             &     15:04:45     & \textbf{  Log-Likelihood:    } &   -255.98   \\
+\textbf{No. Observations:} &         262      & \textbf{  AIC:               } &     516.0   \\
+\textbf{Df Residuals:}     &         260      & \textbf{  BIC:               } &     523.1   \\
+\textbf{Df Model:}         &           1      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                   & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{Intercept} &      11.4630  &        0.080     &   143.363  &         0.000        &        11.306    11.620       \\
+\textbf{id}        &      -0.0202  &        0.001     &   -38.287  &         0.000        &        -0.021    -0.019       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 22.352 & \textbf{  Durbin-Watson:     } &    0.989  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &   25.530  \\
+\textbf{Skew:}          &  0.712 & \textbf{  Prob(JB):          } & 2.86e-06  \\
+\textbf{Kurtosis:}      &  3.558 & \textbf{  Cond. No.          } &     304.  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+Does it looks great? We have high $R^2$ and very significance on model and coefficient both. But if we compute 
+$\hat{p},\hat{n}$ from  estimated $\log{\hat{p}}, \log{\hat{n}}$ , we got:
 
@@
 The $\hat{n}$ looks too small and $\hat{p}$ looks too big as we notice the quick fall of sequence head that
-can not be expressed the too small $\hat{p}$ as the fit graph illustrate:
+can not be caught by too small $\hat{p}$, as the fit graph illustrate:
 
@@
 
-We can verify this by to regress data chunks separately, 
-obviousily if the model is true, $\hat{p}$ will only change little subject to random noise. 
+We also can verify this by running a piecewise regression:
+
+\[
+S_j = \log(n_1) +  \log(p_1) \mathrm{I}(j<K) j + \log(n_2) + \log(p_2) \mathrm{I}(j \ge K)j + \epsilon_j
+\]
+
+The I(j<K) is indicative function, that take $1$ if the statement included in parenthesis is true otherwise take 0.
+
+Obviousily if the model is true, $\hat{p}$ will only change little subject to random noise. 
 Below results are obtained by taken first $1/10$ data and last $9/10$ data separately:
 
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}    &    log(solve)    & \textbf{  R-squared:         } &     0.887   \\
+\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.886   \\
+\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     677.2   \\
+\textbf{Date:}             & Thu, 11 May 2017 & \textbf{  Prob (F-statistic):} & 5.95e-122   \\
+\textbf{Time:}             &     22:17:31     & \textbf{  Log-Likelihood:    } &   -217.95   \\
+\textbf{No. Observations:} &         262      & \textbf{  AIC:               } &     443.9   \\
+\textbf{Df Residuals:}     &         258      & \textbf{  BIC:               } &     458.2   \\
+\textbf{Df Model:}         &           3      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+             & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{lC}  &      12.9522  &        0.231     &    56.072  &         0.000        &        12.497    13.407       \\
+\textbf{lid} &      -0.0741  &        0.016     &    -4.770  &         0.000        &        -0.105    -0.044       \\
+\textbf{rC}  &      11.0358  &        0.085     &   130.136  &         0.000        &        10.869    11.203       \\
+\textbf{rid} &      -0.0178  &        0.001     &   -33.447  &         0.000        &        -0.019    -0.017       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 27.715 & \textbf{  Durbin-Watson:     } &    1.318  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &   38.377  \\
+\textbf{Skew:}          &  0.699 & \textbf{  Prob(JB):          } & 4.64e-09  \\
+\textbf{Kurtosis:}      &  4.249 & \textbf{  Cond. No.          } & 1.01e+03  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+So we got:
+
 \[
-\hat{p_1} = 0.9275 \quad \hat{p_2} = 0.9824
+\hat{p_1} = 0.9285 \quad \hat{p_2} = 0.9823
 \]
 
-% Let us merge the two fitting result into a unique figure:
+Let us show the two fitting figure:
+
+\begin{figure}[h]
+
+\centering
+
+\subfigure[Piecewise regression]{\includegraphics[width=0.49\linewidth]{bi-regress.png}}
+\subfigure[Log scale]{\includegraphics[width=0.49\linewidth]{bi-regress-log.png}}
+
+\end{figure}
+
+I can't torlerate the odd piecewise regression, although it fit data ok, but it seems to imply that the problem chunks
+adapt different mechanism. Perhaps it's true, but the dangrous of overfitting hidden behind can be achieved by 
+repeating piecewise process.
+
+Now, let's introduce my initialization idea, how does the two order mix model compare to the single id-order model?
+
+We do the optimization:
+
+\begin{align*}
+\min_{n_1,n_2,p} & \quad \E\sum_{j=1}^N (S_j - \hat{S_j})^2 \\
+\textrm{s.t.}    & \quad n_1 \in N \\
+                 & \quad n_2 \in N \\
+                 & \quad p \in [0,1]
+\end{align*}
+
+As you can image, I got very unsteady fitting result due to the similarity between the two orders, and it's analogous
+to multicolinearity. The data broke my ambition cruely. \footnote{I write the paper and experiment at same time,
+I found some result that is beyond my expectations. Since the the value of the paper is very limit and cost is too high
+(you see, my English is not very well), I will not pay more time to rewrite something.}
+
+\section{The time series view}
+
+Considering $S_j$ as time series looks little strange, since obviousily we are dealing a snapshot or intersect data
+that can be observed many times in principe \footnote{In fact, because data I used is scraped in 2016 by my early
+crawler program, I can get another(current time) data to run panel model or otherthing if I want to be. Well, 
+but I don't want pay time to work on another boring crawler program, although it conflict my early talk 
+in presentation.}.
+
+\section{Detecting effect of difficulty}
+
+Maybe it was putting cart before horse. My initialization idea tend to design probility model and reduce it to 
+OLS or other model
 

### 2017-05-12 paper.tex
last two day...

@@
 
-The I(j<K) is indicative function, that take $1$ if the statement included in parenthesis is true otherwise take 0.
+The $I(j < K)$ is indicative function, that take $1$ if the statement included in parenthesis is true otherwise take 0.
 
@@
 
-Considering $S_j$ as time series looks little strange, since obviousily we are dealing a snapshot or intersect data
-that can be observed many times in principe \footnote{In fact, because data I used is scraped in 2016 by my early
-crawler program, I can get another(current time) data to run panel model or otherthing if I want to be. Well, 
-but I don't want pay time to work on another boring crawler program, although it conflict my early talk 
-in presentation.}.
+Considering $S_j$ as time series looks little strange, since obviousily we are dealing a snapshot or cross section 
+datathat can be observed many times in principe \footnote{In fact, because data I used is scraped in 2016 
+by my early crawler program, I can get another(current time) data to run panel model or otherthing 
+if I want to be. Well, but I don't want pay time to work on another boring crawler program, 
+although it conflict my early speaking in presentation.}.
 
-\section{Detecting effect of difficulty}
+We will reduce our scope of discussion into autoregression in this section. Assurming there's a \textit{force}
+that is effected by \textit{time}(id order) and difficulty. Since the latter problem solving situation
+is only caused by few delay item, the difficulty will cause a permanent shock for solving series.
 
-Maybe it was putting cart before horse. My initialization idea tend to design probility model and reduce it to 
-OLS or other model
+\subsection{Ground model}
 
-\section{Motivation}
+The ground model specification is:
 
-Motivation content.
+\[
+solve_i = \beta_0 + \beta_1 solve_{i-1} + \epsilon_i
+\]
+
+The result is:
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}    &      solve       & \textbf{  R-squared:         } &     0.958   \\
+\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.958   \\
+\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     5951.   \\
+\textbf{Date:}             & Fri, 12 May 2017 & \textbf{  Prob (F-statistic):} & 1.05e-180   \\
+\textbf{Time:}             &     22:16:44     & \textbf{  Log-Likelihood:    } &   -2816.2   \\
+\textbf{No. Observations:} &         261      & \textbf{  AIC:               } &     5636.   \\
+\textbf{Df Residuals:}     &         259      & \textbf{  BIC:               } &     5644.   \\
+\textbf{Df Model:}         &           1      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                   & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{Intercept} &    2004.0414  &      796.786     &     2.515  &         0.013        &       435.037  3573.046       \\
+\textbf{$solve\_l1$}  &       0.8586  &        0.011     &    77.142  &         0.000        &         0.837     0.881       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 74.396 & \textbf{  Durbin-Watson:     } &     2.390  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &   869.448  \\
+\textbf{Skew:}          &  0.739 & \textbf{  Prob(JB):          } & 1.59e-189  \\
+\textbf{Kurtosis:}      & 11.818 & \textbf{  Cond. No.          } &  7.82e+04  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+The fitting figure:
+
+\begin{figure}[h]
+
+\centering
+
+\subfigure[Autoregression fitting]{\includegraphics[width=0.49\linewidth]{ar1.png}}
+\subfigure[Log scale]{\includegraphics[width=0.49\linewidth]{ar1-log.png}}
+
+\end{figure}
+
+The figure looks not very nice since the piecewise pattern occurs again.
+
+\subsection{Detecting effect of difficulty}
+
+Maybe it was putting cart before horse. My initialization idea is to try to design probility model that has more 
+realistic meaning and then to simplify it to a OLS or other model. But I found it is easily achived in time series like model,
+althougn it has lack of interpretability. \footnote{The mysterious word \textit{force} may lead to a moving 
+story that call for deep thought, I prefer to act as crowds standing in front of nude King instead of the honest child.}
+
+I set dummy variable $hard$ that take 1 if the difficulty index of corresponding problem is greater than 30 
+otherwise it take 0.
+
+\[
+solve_i = \beta_0 + \beta_1 solve_{i-1} + \beta_2 hard \, solve_{i-1} + \epsilon_i
+\]
+
+The result is:
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.961   \\
+\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.961   \\
+\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     3190.   \\
+\textbf{Date:}              & Fri, 12 May 2017 & \textbf{  Prob (F-statistic):} & 1.13e-182   \\
+\textbf{Time:}              &     23:06:33     & \textbf{  Log-Likelihood:    } &   -2807.0   \\
+\textbf{No. Observations:}  &         261      & \textbf{  AIC:               } &     5620.   \\
+\textbf{Df Residuals:}      &         258      & \textbf{  BIC:               } &     5631.   \\
+\textbf{Df Model:}          &           2      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{Intercept}          &    3928.8190  &      888.898     &     4.420  &         0.000        &      2178.399  5679.239       \\
+\textbf{solve\_l1}           &       0.8508  &        0.011     &    77.956  &         0.000        &         0.829     0.872       \\
+\textbf{hard  solve\_l1} &      -0.8225  &        0.189     &    -4.345  &         0.000        &        -1.195    -0.450       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 75.418 & \textbf{  Durbin-Watson:     } &     2.343  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1059.431  \\
+\textbf{Skew:}          &  0.688 & \textbf{  Prob(JB):          } & 8.86e-231  \\
+\textbf{Kurtosis:}      & 12.774 & \textbf{  Cond. No.          } &  9.01e+04  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+Does a hard problem decrease "keep rate" from $85.08\%$ to $2.82\%$ actually? Since the first "hard" problem appear
+82th location. The fact is hidden in detailed tail figure:
+
+\includegraphics[scale=0.55]{tail.png}
+
+Well, it show a good reason why a standard AR model don't have a intercept term. Let's drop the intercept term and
+regress it.
+
+\[
+solve_i = \beta_1 solve_{i-1} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}    &      solve       & \textbf{  R-squared:         } &     0.965   \\
+\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.965   \\
+\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     7133.   \\
+\textbf{Date:}             & Fri, 12 May 2017 & \textbf{  Prob (F-statistic):} & 5.01e-191   \\
+\textbf{Time:}             &     23:44:00     & \textbf{  Log-Likelihood:    } &   -2819.4   \\
+\textbf{No. Observations:} &         261      & \textbf{  AIC:               } &     5641.   \\
+\textbf{Df Residuals:}     &         260      & \textbf{  BIC:               } &     5644.   \\
+\textbf{Df Model:}         &           1      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                  & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1} &       0.8698  &        0.010     &    84.458  &         0.000        &         0.850     0.890       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 62.426 & \textbf{  Durbin-Watson:     } &     2.362  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &   945.115  \\
+\textbf{Skew:}          &  0.399 & \textbf{  Prob(JB):          } & 5.90e-206  \\
+\textbf{Kurtosis:}      & 12.288 & \textbf{  Cond. No.          } &      1.00  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+It seems very like to original model.
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 hard \, solve_{i-1} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.966   \\
+\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.965   \\
+\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     3634.   \\
+\textbf{Date:}              & Fri, 12 May 2017 & \textbf{  Prob (F-statistic):} & 3.17e-190   \\
+\textbf{Time:}              &     23:42:11     & \textbf{  Log-Likelihood:    } &   -2816.6   \\
+\textbf{No. Observations:}  &         261      & \textbf{  AIC:               } &     5637.   \\
+\textbf{Df Residuals:}      &         259      & \textbf{  BIC:               } &     5644.   \\
+\textbf{Df Model:}          &           2      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}           &       0.8713  &        0.010     &    85.207  &         0.000        &         0.851     0.891       \\
+\textbf{diff\_hard:solve\_l1} &      -0.4055  &        0.170     &    -2.387  &         0.018        &        -0.740    -0.071       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 61.517 & \textbf{  Durbin-Watson:     } &     2.290  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1185.953  \\
+\textbf{Skew:}          &  0.215 & \textbf{  Prob(JB):          } & 2.98e-258  \\
+\textbf{Kurtosis:}      & 13.434 & \textbf{  Cond. No.          } &      16.6  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+Ok, this one seems better than the model with intercept. The "hard" problem only decrease "keep rate" 
+from $87.13\%$ to $46.57\%$.
+
+\subsection{Dectecting skip effect}
+
+\subsection{Dectecting phase effect}
+
+We would like to see the later problem tend to face to buru solver, so the difficulty effect will decrease.
+
+\section{Conclusion}
+
+Conclusion content.
 

### 2017-05-13 paper.tex
Windows cracks again, let me backup it as soon as possible.

@@
 \[
-solve_i = \beta_1 solve_{i-1} + \beta_2 hard \, solve_{i-1} + \epsilon_i
+solve_i = \beta_1 solve_{i-1} + \beta_2 hard_i \, solve_{i-1} + \epsilon_i
 \]
@@
 
+If a solver encounter a hard problem that he can't solve, he may drop the website or wait to time that he can
+solve it, that is what above model want to match. But we can consider another behavior in which solver will
+try to skip the problem and to solve the next one. If the hard problem is \textit{isolated}, we can expect
+the decrease shock caused by the problem will be compressd. For match this, I specify the 2 lag item:
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 hard_i \, solve_{i-1} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.961   \\
+\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.960   \\
+\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     2099.   \\
+\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 2.30e-180   \\
+\textbf{Time:}              &     09:37:24     & \textbf{  Log-Likelihood:    } &   -2797.0   \\
+\textbf{No. Observations:}  &         260      & \textbf{  AIC:               } &     5600.   \\
+\textbf{Df Residuals:}      &         257      & \textbf{  BIC:               } &     5611.   \\
+\textbf{Df Model:}          &           3      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}           &       0.6957  &        0.060     &    11.564  &         0.000        &         0.577     0.814       \\
+\textbf{solve\_l2}           &       0.1718  &        0.053     &     3.230  &         0.001        &         0.067     0.277       \\
+\textbf{diff\_hard:solve\_l1} &      -0.3490  &        0.166     &    -2.101  &         0.037        &        -0.676    -0.022       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 76.644 & \textbf{  Durbin-Watson:     } &    2.015  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } & 2966.655  \\
+\textbf{Skew:}          & -0.202 & \textbf{  Prob(JB):          } &     0.00  \\
+\textbf{Kurtosis:}      & 19.543 & \textbf{  Cond. No.          } &     22.4  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 hard_i \, solve_{i-1} + \beta_4 hard \, solve_{i-2} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.961   \\
+\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.960   \\
+\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     1569.   \\
+\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 1.03e-178   \\
+\textbf{Time:}              &     09:38:11     & \textbf{  Log-Likelihood:    } &   -2796.8   \\
+\textbf{No. Observations:}  &         260      & \textbf{  AIC:               } &     5602.   \\
+\textbf{Df Residuals:}      &         256      & \textbf{  BIC:               } &     5616.   \\
+\textbf{Df Model:}          &           4      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}           &       0.7014  &        0.061     &    11.406  &         0.000        &         0.580     0.822       \\
+\textbf{solve\_l2}           &       0.1667  &        0.054     &     3.064  &         0.002        &         0.060     0.274       \\
+\textbf{diff\_hard:solve\_l1} &      -0.4368  &        0.253     &    -1.727  &         0.085        &        -0.935     0.061       \\
+\textbf{diff\_hard:solve\_l2} &       0.1235  &        0.268     &     0.461  &         0.645        &        -0.405     0.652       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 75.816 & \textbf{  Durbin-Watson:     } &    2.022  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } & 2893.093  \\
+\textbf{Skew:}          & -0.178 & \textbf{  Prob(JB):          } &     0.00  \\
+\textbf{Kurtosis:}      & 19.338 & \textbf{  Cond. No.          } &     46.5  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 hard_i \, solve_{i-1} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.968   \\
+\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.967   \\
+\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     1910.   \\
+\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 1.06e-188   \\
+\textbf{Time:}              &     09:52:21     & \textbf{  Log-Likelihood:    } &   -2745.4   \\
+\textbf{No. Observations:}  &         259      & \textbf{  AIC:               } &     5499.   \\
+\textbf{Df Residuals:}      &         255      & \textbf{  BIC:               } &     5513.   \\
+\textbf{Df Model:}          &           4      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}           &       0.5798  &        0.054     &    10.823  &         0.000        &         0.474     0.685       \\
+\textbf{solve\_l2}           &       0.1711  &        0.062     &     2.741  &         0.007        &         0.048     0.294       \\
+\textbf{solve\_l3}           &       0.1300  &        0.046     &     2.809  &         0.005        &         0.039     0.221       \\
+\textbf{diff\_hard:solve\_l1} &      -0.3202  &        0.142     &    -2.247  &         0.025        &        -0.601    -0.040       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 94.148 & \textbf{  Durbin-Watson:     } &     2.375  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1219.969  \\
+\textbf{Skew:}          &  1.042 & \textbf{  Prob(JB):          } & 1.22e-265  \\
+\textbf{Kurtosis:}      & 13.426 & \textbf{  Cond. No.          } &      26.1  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 solve_{i-4} + \beta_5 hard_i \, solve_{i-1} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}     &      solve       & \textbf{  R-squared:         } &     0.973   \\
+\textbf{Model:}             &       OLS        & \textbf{  Adj. R-squared:    } &     0.972   \\
+\textbf{Method:}            &  Least Squares   & \textbf{  F-statistic:       } &     1820.   \\
+\textbf{Date:}              & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 4.90e-196   \\
+\textbf{Time:}              &     09:52:27     & \textbf{  Log-Likelihood:    } &   -2697.7   \\
+\textbf{No. Observations:}  &         258      & \textbf{  AIC:               } &     5405.   \\
+\textbf{Df Residuals:}      &         253      & \textbf{  BIC:               } &     5423.   \\
+\textbf{Df Model:}          &           5      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                            & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}           &       0.3339  &        0.055     &     6.110  &         0.000        &         0.226     0.442       \\
+\textbf{solve\_l2}           &       0.2081  &        0.055     &     3.776  &         0.000        &         0.100     0.317       \\
+\textbf{solve\_l3}           &       0.0363  &        0.055     &     0.660  &         0.510        &        -0.072     0.145       \\
+\textbf{solve\_l4}           &       0.2581  &        0.041     &     6.323  &         0.000        &         0.178     0.338       \\
+\textbf{diff\_hard:solve\_l1} &      -0.2193  &        0.124     &    -1.767  &         0.079        &        -0.464     0.025       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 135.383 & \textbf{  Durbin-Watson:     } &    2.179  \\
+\textbf{Prob(Omnibus):} &   0.000 & \textbf{  Jarque-Bera (JB):  } & 1713.428  \\
+\textbf{Skew:}          &   1.761 & \textbf{  Prob(JB):          } &     0.00  \\
+\textbf{Kurtosis:}      &  15.123 & \textbf{  Cond. No.          } &     29.1  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+To compare the four models, we can see the difficulty shock only exists one period (So solver can't
+recall the hell except that is the last problem he try to solve.). And there's significance skip effect, I prefer
+to choose the model 3 as real model, hence we can get the average transition diagram
+from the estimated parameters to illustrate this:
+
+\[
+\begin{array}{c|ccccccc}
+\mathrm{Hard} & 1 & 2& 3 & 4 & 5 & 6 &7 \\
+\hline
+\mathrm{EEEE} & 10000 & 9500 & 9000 & 8593 & 8164 & 7749 & 7386 \\
+\mathrm{EEEH} & 10000 & 9500 & 9000 & 8593 & 8164 & 7749 & 4905 \\
+\mathrm{EEHE} & 10000 & 9500 & 9000 & 8593 & 8164 & 5135 & 7046 \\
+\mathrm{EEHH} & 10000 & 9500 & 9000 & 8593 & 8164 & 5135 & 5402 \\
+\mathrm{EHEE} & 10000 & 9500 & 9000 & 8593 & 5413 & 7392 & 6869 \\
+\mathrm{EHEH} & 10000 & 9500 & 9000 & 8593 & 5413 & 7392 & 4502 \\
+\mathrm{EHHE} & 10000 & 9500 & 9000 & 8593 & 5413 & 5658 & 6644 \\
+\mathrm{EHHH} & 10000 & 9500 & 9000 & 8593 & 5413 & 5658 & 4832 \\
+\mathrm{HEEE} & 10000 & 9500 & 9000 & 5711 & 7790 & 7208 & 5581 \\
+\mathrm{HEEH} & 10000 & 9500 & 9000 & 5711 & 7790 & 7208 & 3273 \\
+\mathrm{HEHE} & 10000 & 9500 & 9000 & 5711 & 7790 & 4713 & 5257 \\
+\mathrm{HEHH} & 10000 & 9500 & 9000 & 5711 & 7790 & 4713 & 3748 \\
+\mathrm{HHEE} & 10000 & 9500 & 9000 & 5711 & 5961 & 6970 & 5237 \\
+\mathrm{HHEH} & 10000 & 9500 & 9000 & 5711 & 5961 & 6970 & 3006 \\
+\mathrm{HHHE} & 10000 & 9500 & 9000 & 5711 & 5961 & 5061 & 4989 \\
+\mathrm{HHHH} & 10000 & 9500 & 9000 & 5711 & 5961 & 5061 & 3369 \\
+\end{array}
+\]
+
+The $\mathrm{H}$ means that the corresponding problem is "hard", the $\mathrm{E}$ means that the corresponding
+problem is not "hard". We can observe the obvious skip effect at all.
+
 \subsection{Dectecting phase effect}
 
-We would like to see the later problem tend to face to buru solver, so the difficulty effect will decrease.
+We would like to see the later problem tend to facing buru solver, so the difficulty effect will decrease.
+
+I use dummy variable like above discussion again, even thougn a countinuous decrease tendency is expected,
+but I can't see a method that can transform it to a linear model easily.
+
+The model specification is:
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 hard \, solve_{i-1} +
+		  \beta_5 hard_i \, right_i \, solve_{i-1} + \epsilon_i
+\]
+
+The dummy variable $left_i$ take 1 if the ith problem is in second half part.
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}           &      solve       & \textbf{  R-squared:         } &     0.968   \\
+\textbf{Model:}                   &       OLS        & \textbf{  Adj. R-squared:    } &     0.967   \\
+\textbf{Method:}                  &  Least Squares   & \textbf{  F-statistic:       } &     1523.   \\
+\textbf{Date:}                    & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 4.62e-187   \\
+\textbf{Time:}                    &     14:03:17     & \textbf{  Log-Likelihood:    } &   -2745.3   \\
+\textbf{No. Observations:}        &         259      & \textbf{  AIC:               } &     5501.   \\
+\textbf{Df Residuals:}            &         254      & \textbf{  BIC:               } &     5518.   \\
+\textbf{Df Model:}                &           5      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                                  & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}                 &       0.5800  &        0.054     &    10.808  &         0.000        &         0.474     0.686       \\
+\textbf{solve\_l2}                 &       0.1706  &        0.063     &     2.728  &         0.007        &         0.047     0.294       \\
+\textbf{solve\_l3}                 &       0.1303  &        0.046     &     2.809  &         0.005        &         0.039     0.222       \\
+\textbf{diff\_hard:solve\_l1}       &      -0.3482  &        0.163     &    -2.131  &         0.034        &        -0.670    -0.026       \\
+\textbf{diff\_hard:solve\_l1:right} &       0.1162  &        0.329     &     0.353  &         0.725        &        -0.532     0.765       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 94.967 & \textbf{  Durbin-Watson:     } &     2.375  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1216.730  \\
+\textbf{Skew:}          &  1.059 & \textbf{  Prob(JB):          } & 6.17e-265  \\
+\textbf{Kurtosis:}      & 13.405 & \textbf{  Cond. No.          } &      62.1  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+So we can confirm that it is true that solver try to solve latter problem has more steady belief.
+The dummy variable method can't be used futher since the condition number has implies the rise of multicolinearity.
 
@@
 
-Conclusion content.
+I have build a more realistic probility model and fail to extend it as you see. 
+Then I develope a indirect time series like model to verify some hypothesis. I can draw conclusion from these survey:
+
+1. Difficulty shock exists significance but it has not memory 
+2. The boru solver seems stable more than raw solver when they encounter hard problem.
 

### 2017-05-13 paper.tex
complete class paper

@@
 \title{The User Behavior On Online Judge Website}
-\author{yueyi zhuo}
+\author{yueyi zhuo (2014060843)}
 %\institute{School of Mathematical,Sichuan Normal University}
@@
 
-Abstract content.
+In this paper, I develope two types of model to investigate Online Judge website solve record 
+and verify some factor holded by order, solver and problem difficulty structure.
 
@@
 
-\section{The time series view}
+\section{The time series like model}
 
@@
 
+The fitting figure is:
+
+\includegraphics[scale=0.55]{tail2.png}
+
 Ok, this one seems better than the model with intercept. The "hard" problem only decrease "keep rate" 
@@
 try to skip the problem and to solve the next one. If the hard problem is \textit{isolated}, we can expect
-the decrease shock caused by the problem will be compressd. For match this, I specify the 2 lag item:
+the decrease shock caused by the problem will be compressd. For match this, I try to specify the more lag item:
 
@@
 So we can confirm that it is true that solver try to solve latter problem has more steady belief.
-The dummy variable method can't be used futher since the condition number has implies the rise of multicolinearity.
+The dummy variable method can't be used futher since the condition number has implies the rise of multicolinearity,
+thus we get a unsignicant result. But if I replace dummy variable $hard$ to original fake quantity $diff$ variable,
+replace $right$ to original order variable $id$, we can get a signicant result:
+
+\[
+solve_i = \beta_1 solve_{i-1} + \beta_2 solve_{i-2} + \beta_3 solve_{i-3} + \beta_4 diff \, solve_{i-1} +
+		  \beta_5 diff \, id \, solve_{i-1} + \epsilon_i
+\]
+
+\begin{center}
+\begin{tabular}{lclc}
+\toprule
+\textbf{Dep. Variable:}    &      solve       & \textbf{  R-squared:         } &     0.970   \\
+\textbf{Model:}            &       OLS        & \textbf{  Adj. R-squared:    } &     0.969   \\
+\textbf{Method:}           &  Least Squares   & \textbf{  F-statistic:       } &     1619.   \\
+\textbf{Date:}             & Sat, 13 May 2017 & \textbf{  Prob (F-statistic):} & 2.34e-190   \\
+\textbf{Time:}             &     14:47:52     & \textbf{  Log-Likelihood:    } &   -2737.6   \\
+\textbf{No. Observations:} &         259      & \textbf{  AIC:               } &     5485.   \\
+\textbf{Df Residuals:}     &         254      & \textbf{  BIC:               } &     5503.   \\
+\textbf{Df Model:}         &           5      & \textbf{                     } &             \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lccccc}
+                          & \textbf{coef} & \textbf{std err} & \textbf{t} & \textbf{P$>$$|$t$|$} & \textbf{[95.0\% Conf. Int.]}  \\
+\midrule
+\textbf{solve\_l1}         &       0.7618  &        0.068     &    11.162  &         0.000        &         0.627     0.896       \\
+\textbf{solve\_l2}         &       0.1196  &        0.062     &     1.931  &         0.055        &        -0.002     0.242       \\
+\textbf{solve\_l3}         &       0.1470  &        0.045     &     3.245  &         0.001        &         0.058     0.236       \\
+\textbf{solve\_l1:diff}    &      -0.0302  &        0.008     &    -3.921  &         0.000        &        -0.045    -0.015       \\
+\textbf{solve\_l1:diff:id} &       0.0001  &     5.47e-05     &     2.705  &         0.007        &      4.02e-05     0.000       \\
+\bottomrule
+\end{tabular}
+\begin{tabular}{lclc}
+\textbf{Omnibus:}       & 98.904 & \textbf{  Durbin-Watson:     } &     2.245  \\
+\textbf{Prob(Omnibus):} &  0.000 & \textbf{  Jarque-Bera (JB):  } &  1333.652  \\
+\textbf{Skew:}          &  1.107 & \textbf{  Prob(JB):          } & 2.52e-290  \\
+\textbf{Kurtosis:}      & 13.894 & \textbf{  Cond. No.          } &  4.16e+03  \\
+\bottomrule
+\end{tabular}
+%\caption{OLS Regression Results}
+\end{center}
+
+This imply a continual decline of effect of difficulty shock.
 
@@
 
-I have build a more realistic probility model and fail to extend it as you see. 
+I have built a more realistic probility model and fail to extend it as you see. 
 Then I develope a indirect time series like model to verify some hypothesis. I can draw conclusion from these survey:
@@
 1. Difficulty shock exists significance but it has not memory
+
 2. The boru solver seems stable more than raw solver when they encounter hard problem.
 
+From result, I can point out that OJ website should place their difficulty problem into proper(latter)
+ location to match solver structure to maximize their business and activity.
+
 \end{document}
